%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%	 	Copyright (c) 2021 		  %
%		   Daylam Tayari 		  %
%								  %
%  Credit to Pascal-0x90 for this  %
% 	  Latex resume template.		  %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass{article}
\usepackage[cm]{fullpage}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage{fontawesome5}
\hypersetup{breaklinks=true,%
pagecolor=white,%
colorlinks=true,%
linkcolor=cyan,%
urlcolor=MyDarkBlue}
\definecolor{MyDarkBlue}{rgb}{0,0.0,0.45}


%%%%%%%%%%%%%%%%%%%%%%%%%%
% Formatting parameters  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newlength{\tabin}
\setlength{\tabin}{1em}
\newlength{\secsep}
\setlength{\secsep}{0.1cm}
\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}
\definecolor{contactgray}{gray}{0.2}
\pagestyle{empty}


%%%%%%%%%%%%%%%%%%%%%%%%%%
%  Template Definitions  %
%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\lineunder}{\vspace*{-8pt} \\ \hspace*{-6pt} \hrulefill \\ \vspace*{-15pt}}
\newcommand{\name}[1]{\begin{center}\textsc{\Large#1}\\\end{center}}
\newcommand{\program}[1]{\begin{center}\textsc{#1}\end{center}}
\newcommand{\contact}[1]{\begin{center}\color{contactgray}{\normalsize#1}\end{center}}

\newenvironment{tabbedsection}[1]{
  \begin{list}{}{
      \setlength{\itemsep}{0pt}
      \setlength{\labelsep}{0pt}
      \setlength{\labelwidth}{0pt}
      \setlength{\leftmargin}{\tabin}
      \setlength{\rightmargin}{\tabin}
      \setlength{\listparindent}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\parskip}{0pt}
      \setlength{\partopsep}{0pt}
      \setlength{\topsep}{#1}
    }
  \item[]
}{\end{list}}

\newenvironment{nospacetabbing}{
    \begin{tabbing}
}{\end{tabbing}\vspace{-1.2em}}

\newenvironment{resume_header}{}{\vspace{0pt}}

\newenvironment{resume_section}[1]{
  \filbreak
  \vspace{2\secsep}
  \textsc{\color{blue}\large#1}
  \lineunder
  \begin{tabbedsection}{\secsep}
}{\end{tabbedsection}}

\newenvironment{resume_subsection}[2][]{
  \textbf{\color{BlueViolet}#2} \hfill {\normalsize #1} \hspace{-5em} 
  \begin{tabbedsection}{0.5\secsep}
}{\end{tabbedsection}}

\newenvironment{subitems}{
  \renewcommand{\labelitemi}{-}
  \begin{itemize}
      \setlength{\labelsep}{1em}
}{\end{itemize}}

\newenvironment{resume_employer}[4]{
  \vspace{\secsep}
  \textbf{#1} \\ 
  \indent {\normalsize #2} \hfill {\normalsize #3 (#4)}
  \begin{tabbedsection}{0pt}
  \begin{subitems}
}{\end{subitems}\end{tabbedsection}}


%%%%%%%%%%%%%%%%%%%%
%     Document     %
%%%%%%%%%%%%%%%%%%%%

\begin{document}

\begin{resume_header}
\name{Daylam Tayari}
\contact {
\faEnvelope[solid] \, \href{mailto:daylamtayari@tayari.gg}{daylamtayari@tayari.gg}
\hspace{1cm} \faLinkedin \, \href{https://www.linkedin.com/in/daylamtayari}{daylamtayari}
\hspace{1cm} \faGitlab \, \href{https://git.tayari.gg/tayari/Resume}{git.tayari.gg/tayari}
%\hspace{1cm} \faGlobe \, \href{https://tayari.gg}{tayari.gg}
}
\end{resume_header}

\begin{resume_section}{Objective}
Highly driven student who is able to easily adapt to ever-changing situations with experience developing numerous projects across a variety of technologies and enterprise solutions seeking a junior-level security or developer position.
\end{resume_section}

\begin{resume_section}{Education}
  \begin{resume_subsection}[(August 2020 - May 2023 {[Expected]})]{Arizona State University}
    B.S. Computer Science (Cybersecurity concentration) \hspace{5.05cm} GPA: 3.31\\*
  \end{resume_subsection}
\end{resume_section}

\vspace{-3\secsep}

\begin{resume_section}{Skills}
	\begin{nospacetabbing}
  	\textbf{Languages:} \hspace{5em} \=Java, Python, C++, C, SQL, JavaScript, HTML, CSS.\\*
  	\textbf{Technologies:} \> PostgreSQL, GraphQL, Metasploit, Docker, NodeJS, Burp Suite, Proxmox.\\*
  	\textbf{Miscellaneous:} \> Cloud services (AWS and Oracle), GNU/Linux, Bash, Git, Latex, Autodesk Inventor.\\*
  	\textbf{Foreign Languages:} \> Native French speaker, fully bilingual in French \& English.\\*
    \textbf{Work Authorization:} \> United States green card holder.\\*
  \end{nospacetabbing}  
\end{resume_section}

\vspace{2\secsep}

\begin{resume_section}{Projects}
	\begin{resume_subsection}[(August 2021 - Present)]{Curated ICO}
		\begin{subitems}
            \item After identifying a need in the cryptocurrency space, developing a data aggregation and analysis platform in a coordinated team environment to assist investors in discovering new but trustworthy cryptocurrencies.
            \item Designed and deployed a PostgreSQL database paired with a correlating GraphQL API in order to store large collections of financial data and allow for their rapid retrieval by users. 
            \item Developed an automated data retrieval tool with a runtime of 9.5ms that fetches financial data on cryptocurrencies via APIs and inputs them into a database using a GraphQL API to perform historical analysis. 
		\end{subitems}
	\end{resume_subsection}
	\vspace{2\secsep}
	\begin{resume_subsection}[(February 2021)]{To-Do Export - \faGitlab \hspace{0.01cm} \href{https://git.tayari.gg/tayari/Microsoft-To-Do-Export}{git.tayari.gg/tayari/Microsoft-To-Do-Export}}
  		\begin{subitems} 
            \item Frustrated by a total lack of any export solutions for the Microsoft To-Do program, devised and developed a custom solution that exports all task lists into a format compatible to be imported directly into other task management applications.
  			\item Developed in Java and utilizes REST APIs to retrieve the task lists which are then converted into the appropriate CSV and JSON formats in order to ensure compatibility with other task management applications.
    		\end{subitems}
  	\end{resume_subsection}
  	\vspace{2\secsep}
	\begin{resume_subsection}[(December 2020 - Present)]{Twitch Recover - \faGithub \hspace{0.01cm} \href{https://github.com/twitchrecover/twitchrecover}{github.com/twitchrecover/twitchrecover}}  
		\begin{subitems}
                \item Following mass confusion on copyright restrictions, developed a tool that has over 100,000+ downloads that allows users of a popular live streaming platform to better manage and recover their video content.
    			\item Built in Java and utilizes REST and GraphQL APIs to retrieve and feed video content to end users.
    			\item Resolved hundreds of user tickets, performing the relevant support and issue remediation.
		\end{subitems}
	\end{resume_subsection}
	\vspace{2\secsep}
%	\begin{resume_subsection}[(October - November 2020)]{Shadow Realm Bot}
%		\begin{subitems}
%            \item Following the removal of a popular moderation feature, created a livestreaming moderation bot which reimplements that feature allowing content creators to better moderate their communities. 
%			\item Developed a front end in ReactJS utilizing NodeJS packages paired with a SQL database backend.
%			\item Implemented OAuth Authentication for user authentication paired with an API to retrieve the necessary user data and perform the moderation.
%    	\end{subitems}
%	\end{resume_subsection}
	\vspace{2\secsep}
  	\begin{resume_subsection}[(March 2020 - Present)]{Home Network and Security Lab}
  		\begin{subitems}
            \item Continuously advance my skills with enterprise tools and vulnerabilities by virtualizing vulnerable environments and practicing to deploy and configure a large variety of enterprise tools and solutions. 
  			\item Active on TryHackMe, an online platform with labs to practice and enrich my penetration testing skills.
  		\end{subitems}
  	\end{resume_subsection}
\end{resume_section}

\vspace{2\secsep}

\begin{resume_section}{Associations}
  	\begin{resume_subsection}[(August 2020 - Present)]{DevilSec}
        \begin{subitems}
		    \item Member of ASU's cybersecurity club and compete in cybersecurity team tournaments and CTFs.
            \item Part of the CCDC team competing in a national collegiate cyber defense competition.
            \item Competed in the Hivestorm blue team competition and placed in the top 46\% out of hundreds of teams.
        \end{subitems}
  	\end{resume_subsection}
  	\vspace{2\secsep}
  	\begin{resume_subsection}[(August 2020 - Present)]{ASU Linux User's Group (ASULUG)}
        \begin{subitems}
            \item Member of ASU's Linux enthusiast club which hosts talks and informs students on Linux and open source. 
            \item Assisted numerous students with performing tasks across a variety of Linux distributions and technologies.
%            \item Presented a talk on the Qubes operating system explaining its unique architecture, features and uses.
        \end{subitems}
  	\end{resume_subsection}
\end{resume_section}
\end{document}
